\subsection{Conclusion on \gls{wpt} methods}\label{sec:ConclusionWPT}
On the safety concerns \gls{wpt} methods based on fields are safer than radiations ones as the potentials risks are more manageable and localized.

Inductive coupling is dependent on having two conductive coils being close to one and other in order to reach high efficiency. Resonant coupling is more efficient than the inductive coupling, but is still dependent on having two or more conductive coils being close to one and other. Both inductive coupling and resonant coupling are infeasible for the altitude at which an aircraft operates. 

Capacitive coupling suffers from the same distance scaling problems as inductive and resonant coupling. 

Photovoltaic power transfer is found to be impractical and to have lower efficiency than the alternatives.

\gls{wpt} via radio waves is shown to be feasible over long distances and has a potential to be highly efficient.

In table \ref{tab:mcp_cmd_expl}, a summary of the different methods of \gls{wpt} is present.
\begin{table}[h]
	\centering
	\caption{Summary of the different methods of wireless power transfer.}

	\begin{tabularx}{\textwidth}{lXX}
		Method 				& Summary 										\\ \toprule \rowcolor{lightGrey}
		Inductive coupling	& Only high efficiency at short range. 	\\
		Resonant coupling	& Only high efficiency at medium range with additional coils	\\ \rowcolor{lightGrey}
		Capacitive coupling 		& Only effective at short range. \\
		Photovoltaic 		& Long range, medium-low efficiency, impractical \\\rowcolor{lightGrey}
		Microwave			& Long range, high efficiency \\ 
	\end{tabularx}
\end{table}\label{tab:mcp_cmd_expl}

Thus the conclusion of this section is that radio wave \gls{wpt} is the most suitable method at long distance. The photovoltaic method would be feasible over long distances as well, but with a lower efficiency. 

For both of these method to work a high precision is needed when pointing the power transmitter at the drone. In order to achieve this the ground station needs to locate and track the target with a high accuracy and points very precisely at the target. 

With the methods of wireless power transfer researched, the applications of long distance \gls{wpt} will now be analysed. 