\section{Methods of \glsentryshort{wpt}}\label{sec:WPTmethods}
Different methods of \gls{wpt} are studied in order to determine which methods are feasible for long distances.

All the researched \gls{wpt} methods use a similar setup with a transmitting station transferrring power to a receptor via a wireless medium. Four different methods are studied.
 
\input{chapters/Part1/WirelessPowerTransfer/InductiveCoupling.tex}
\input{chapters/Part1/WirelessPowerTransfer/CapacitiveCoupling.tex}

\input{chapters/Part1/WirelessPowerTransfer/PhotovoltaicPowerTransfer.tex}
\input{chapters/Part1/WirelessPowerTransfer/Microwaves.tex}

\subsection{Health and safety concerns}
Magnetic fields can be harmful, at frequencies between 1 - \SI{300}{\hertz} the exposure guideline for a whole human body, states that the exposure should not exceed \SI{60}{\milli\tesla\per f}. In the frequency spectrum from \SI{300}{\hertz} - \SI{30}{\kilo\hertz} the whole or partial body exposure should not exceed \SI{0.2}{\milli\tesla}. For users of pacemakers the limit is \SI{0.1}{\milli\tesla} for frequencies of \SI{60}{\hertz} \cite{web:MagneticFieldSafty}.

The E-field made by some \gls{wpt} methods follows many of the same safety concerns as the once for the Magnetic fields.

Photovoltaic power in a concentrated beam such as a laser can be dangerous for living beings. A \SI{1}{\milli\watt} laser can cause temporary eye damage to a person. If a person is hit directly in the eye with a 10 to \SI{20}{\milli\watt} laser, the person's blink reflex might not be fast enough to avoid eye damage. If the power of the laser is increased further, a burn risk is also introduced. Lasers outputting beams with powers above \SI{250}{\milli\watt} could cause skin burns similar to hot wax \cite{web:LaserSafty}.

Electromagnetic waves can also be dangerous. If biological material is placed in a electromagnetic wave it will experience a dielectric heating. This means that if a person touches or stands around an antenna while a high amount of power is transmitted, this person could get severe burns.

\input{chapters/Part1/WirelessPowerTransfer/ConclusionWirelessPowerTransfer.tex}
